---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.width = 7,
  fig.asp = 0.618,
  fig.align = "center",
  out.width = "100%",
  dpi = 300
)
```

# dfrtheme

<!-- badges: start -->
[![R-CMD-check](https://github.com/dzulfiqarfr/dfrtheme/workflows/R-CMD-check/badge.svg)](https://github.com/dzulfiqarfr/dfrtheme/actions)
<!-- badges: end -->

This is an R package to apply my custom theme on [**ggplot2**](https://ggplot2.tidyverse.org/index.html){target="_blank"} charts.

There are two functions:

* `dfr_theme()` to modify the theme components; and  

* `dfr_convert_font_size()` to convert font size from points (pts) to millimeters (mm).


## Installation

``` r
if (!require("devtools")) install_packages("devtools")
library(devtools)
devtools::install_github("dzulfiqarfr/dfrtheme")
```

## Example

```{r demo, message=FALSE, warning=FALSE}
library(dplyr)
library(ggplot2)
library(ggtext)
library(gapminder)
library(dfrtheme)

gapminder_latest <- dplyr::filter(gapminder, year == last(year))

ggplot(
  gapminder_latest, 
  aes(x = gdpPercap, y = lifeExp, fill = continent)
) +
  geom_point(
    pch = 21,
    color = "white",
    size = 2.5,
    stroke = 0.25,
    alpha = 0.75
  ) +
  geom_text(
    aes(label = country),
    size = dfr_convert_font_size(),
    check_overlap = TRUE,
    hjust = "inward",
    vjust = "inward"
  ) +
  scale_x_log10() +
  labs(
    title = "Countries with higher income have better public health",
    subtitle = paste0(
      "GDP per capita at 2005 international dollars ",
      "and life expectancy in 2007"
    ),
    x = "GDP per capita<br>(log scale)",
    y = "Life expectancy<br>(years)",
    caption = "Source: Gapminder<br>Chart: Dzulfiqar Fathur Rahman"
  ) +
  dfr_theme()
```


## Read also

* Best practices to create a new ggplot2 theme ([read this article](https://ggplot2.tidyverse.org/articles/ggplot2-in-packages.html#ggplot2-in-suggests-1){target="_blank"})

* Understanding text size and resolution in ggplot2 by Christophe Nicault ([read his blog post](https://www.christophenicault.com/post/understand_size_dimension_ggplot2/){target="_blank"})
